---
title: "Schedule"
description: "Schedule"
weight: 1
editor_options: 
  chunk_output_type: console
---


## Course Schedule

```{r schedule-setup, echo=FALSE, warning=FALSE, message=FALSE}
# devtools::install_github("gadenbuie/ggweekly")
library(ggweekly)
library(rlang) # Needed for the ggweekly.R script to work
library(configr)
# source('../../R/ggweekly.R') # Fixes issue with loading PT Sans fonts with PDF output
source('../../R/createICS.R')
library(ggplot2)
library(readxl)
library(lubridate)

options(knitr.kable.NA = '')

semester <- 'Spring 2020'

palette <- c('#8dd3c7','#ffffb3','#bebada','#fb8072','#80b1d3','#fdb462',
			 '#b3de69','#fccde5','#d9d9d9','#bc80bd','#ccebc5','#ffed6f')

lastModified <- format(file.info('../../Schedule.xlsx')[1,]$mtime, '%B %d, %Y %I:%M%p')

meetups <- read_excel('../../Schedule.xlsx', sheet = 'Meetups')
meetups$day <- as.Date(meetups$Date)
meetups$label <- paste0('Meetup ', meetups$StartTime, '\n', meetups$Topic)
# meetups$label <- meetups$Topic
meetups$color <- '#4A235A'
meetups$fill <- NA

officeHours <- read_excel('../../Schedule.xlsx', sheet = 'Office_Hours')
officeHours$day <- as.Date(officeHours$Date)
officeHours$label <- paste0('Office Hours\n', officeHours$StartTime, '')
officeHours$color <- '#145A32'
officeHours$fill <- NA

schedule <- rbind(meetups[,c('day', 'label', 'color', 'fill')],
				  officeHours[,c('day', 'label', 'color', 'fill')])

topics <- read_excel('../../Schedule.xlsx', sheet = 'Schedule')
topics$Start <- as.Date(topics$Start)
topics$End <- as.Date(topics$End)
for(i in 1:nrow(topics)) {
	schedule <- rbind(schedule, data.frame(
		day = topics[i,]$Start,
		label = paste0(topics[i,]$Topic, '\n\n\n'),
		color = '#000000',
		fill = palette[i]
	))
	dates <- seq(topics[i,]$Start, topics[i,]$End, by = 'day')[-1]
	for(j in seq_along(dates)) {
		schedule <- rbind(schedule, data.frame(
			day = dates[j],
			label = NA,
			color = NA,
			fill = palette[i]
		))
	}
}

start_day <- lubridate::floor_date(min(meetups$day), "month")
end_day <- lubridate::ceiling_date(max(meetups$day), "month") - 1
```

*Last updated `r lastModified`. Note: Schedule is subject to change.*

```{r createICS, echo=FALSE, results='hide'}
config <- read.config('../../config.toml')
outDir <- config$publishDir
meetups$starttime <- parse_date_time(paste0(as.character(meetups$Date), ' ', meetups$StartTime),
							    orders = "%Y-%m-%d %H:%M %p", tz = "America/New_York")
meetups$endtime <- parse_date_time(paste0(as.character(meetups$Date), ' ', meetups$EndTime),
								   orders = "%Y-%m-%d %H:%M %p", tz = "America/New_York")
meetups$location <- 'GoToMeeting'
meetups$summary <- meetups$Topic
meetups$description <- ''

ics.file <- paste0('../../', outDir, '/DATA606.ics')
createICS(meetups) %>% write(file = ics.file)
```

[Click here to import the course calendar into your calendar application](/DATA606.ics)

```{r printTopics, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
topics$Start <- format(topics$Start, format = '%A, %B %d, %Y')
topics$End <- format(topics$End, format = '%A, %B %d, %Y')
knitr::kable(topics)
```

## Meetups

There will be weekly meetups. You are encouraged to attend as many as you can but recordings will generally be availabe the day after the meetup.

Please join the meetup from your computer, tablet or smartphone: https://global.gotomeeting.com/join/851198509 

You can also dial in using your phone. United States: +1 (571) 317-3122  
Access Code: 851-198-509 

New to GoToMeeting? Get the app now and be ready when your first meeting starts: 
https://global.gotomeeting.com/install/851198509 


[Presentation Signup Sheet](https://docs.google.com/spreadsheets/d/1ZS-my1__uA6VvJpu8cyS5nsUxrjRPF-vS3_t5xN9Bgw/edit?usp=sharing)

```{r schedule-table, echo=FALSE, results='asis'}
# meetups$Date <- format(meetups$Date, '%a, %b %d')
meetups$Date <- format(meetups$Date, format = '%A, %B %d, %Y')
knitr::kable(meetups[,c('Date','StartTime','Topic','Resources')], )
```


```{r schedule-figure, echo=FALSE, warning=FALSE, message=FALSE}
# ggweek_planner(
# 	start_day = start_day, 
# 	end_day = end_day, 
# 	show_month_boundaries = FALSE, 
# 	show_month_start_day = FALSE,
# 	week_start = "epiweek",
# 	week_start_label = "week",
# 	base_font_family = '',
# 	font_label_text = 'Helvetica',
# 	holidays = NULL,
# 	highlight_days = schedule) +
# 	ggplot2::ggtitle("EPSY 630 - Spring 2020") +  
# 	ggplot2::facet_wrap(~ month, scales = 'free', ncol=1)

schedule$label <- gsub('<br/>', '\n', schedule$label)

months <- seq(start_day, end_day, by = "1 month")
for(i in seq_along(months)) {
	gcal <- ggweek_planner(
		start_day = months[i],
		end_day = months[i] + days_in_month(month(months[i])) - 1,	
		show_month_boundaries = FALSE, 
		show_month_start_day = FALSE,
		week_start = "epiweek",
		week_start_label = "week",
		font_label_family = 'Helvetica',
		holidays = NULL,
		highlight_days = schedule
		) +
		ggplot2::theme(plot.margin = ggplot2::margin(0.5, 0.5, 0.5, 0.5, "in")) +
		ggplot2::ggtitle(paste0('EPSY 630 - ', semester, ' - ', month(months[i], label = TRUE, abbr = FALSE)))
	print(gcal)
}

```
